Evaluation of performances

### 2020-04-29 analysis/eval-performance.Rmd
wflow_publish(knitr_in("analysis/eval-performance.Rmd"), view = FALSE,     verbose = TRUE)

@@

# define appearance of \multirow
df_tbl[[1]][first] <-
  paste0("\\midrule\\multirow{", rle.lengths, "}{*}{\\textbf{", df_tbl[[1]][first], "}}")
df_tbl %>%
  xtable::xtable(
    type = "latex",
    caption = "Percentage of selected features of each fold during optimization for selected learners",
    label = "tab:tune-perc-sel-features"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/tune-perc-sel-features.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )
```

>>>>

```{r, comment="", results="asis", echo=FALSE}
old.hooks <- fansi::set_knit_hooks(knitr::knit_hooks)
```

@@

# define appearance of \multirow
df_tbl[[1]][first] <-
  paste0("\\midrule\\multirow{", rle.lengths, "}{*}{\\textbf{", df_tbl[[1]][first], "}}")
df_tbl %>%
  xtable::xtable(
    type = "latex",
    caption = "Percentage of selected features of each fold during optimization for selected learners",
    label = "tab:tune-perc-sel-features"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/tune-perc-sel-features.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )

df_tbl
```
